---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# sabrenet-rousettus-dynamics

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.6637927)](https://doi.org/10.5281/zenodo.6637927)
[![License (for code): MIT](https://img.shields.io/badge/License (for code)-MIT-green.svg)](https://opensource.org/licenses/MIT)
[![License: CC0-1.0](https://img.shields.io/badge/License (for data)-CC0_1.0-lightgrey.svg)](http://creativecommons.org/publicdomain/zero/1.0/)
[![License: CC-BY-4.0](https://img.shields.io/badge/License (for text)-CC_BY_4.0-blue.svg)](http://creativecommons.org/publicdomain/zero/1.0/)

This repository contains data and R code which are supplements to:

_Viral maintenance and excretion dynamics of coronaviruses within an Egyptian rousette fruit bat colony- considerations for spillover_, by
Geldenhuys et al.  (2022)

Please cite that paper, and/or the Zenodo data reference (<https://doi.org/######>)
when using data or referring to this study.

## Repository Structure and Reproducibility

-   `data/` contains data from the study
    and a data dictionary describing all variables.
-   `R/` contains functions used in this analysis. 
-   `reports/` contains literate code for  R Markdown reports generated in the analysis
-   `outputs/` contains compiled reports and figures.
-   This project uses the [{targets}](https://wlandau.github.io/targets-manual/) 
    framework to organize build steps for analysis pipeline.  The steps are
    defined in the `_targets.R` file and the workflow can be executed by running
    `run.R` via `source("run.R")` in your R terminal or `Rscript run.R` in 
    your system shell.  The schematic figure below summarizes the steps. (The figure is generated using
    `mermaid.js` syntax and should display as a graph on GitHub.  It can also
    be viewed by pasting the code into <https://mermaid.live>.)

```{r, echo=FALSE, message = FALSE, results='asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(targets_only = TRUE, outdated = FALSE, legend = FALSE, color = FALSE, exclude = "readme"),
  "```",
  sep = "\n"
)
```

-   This project requires `r R.version$version.string`. This project uses the [{renv}](https://rstudio.github.io/renv/) framework to 
    record R package dependencies and versions. Packages and versions used are recorded in 
    `renv.lock` and code used to manage dependencies is in `renv/` and other files
    in the root project directory.  On starting an R session in the working directory, run `renv::restore()`
    to install R package dependencies.
