---
output: 
  github_document:
    html_preview: true
  always_allow_html: true
---


```{r setup, include=FALSE}
library(knitr)
library(targets)
tar_load(c(summarized_quantities, svg_plots, png_plots, partial_effect_plots_svg,
           partial_effect_plots_png, raw_prev, model_prev, flextable_gam_summary,
           table_fmi_demo))
```

# Calculated Prevalences

## Raw

Prevalences calculated as a % of number of samples collected, with corrected values for fecal samples

```{r, echo = FALSE}
knitr::kable(raw_prev)
```

## Modeled

Prevalances calculated as baseline (intercept) probability of infection of single samples from the Generalized Additive model, conditional on mean bat and environment variables.

```{r, echo = FALSE}
knitr::kable(model_prev)
```

## Tables

## Body Condition and Prevalence by demographic group

```{r, echo = FALSE}
knitr::kable(table_fmi_demo)
```

# Figures

```{r, results = "asis", echo = FALSE}
cat(paste0("## ", svg_plots, "\n\n![](", basename(svg_plots), ")"), sep = "\n\n")
```

## Partial Effect plots


```{r, results = "asis", echo = FALSE}
cat(paste0("\n\n![](", basename(partial_effect_plots_svg), ")"), sep = "\n\n")
```
